\LARGE \bf Preparation of Papers for IEEE Sponsored Conferences \& Symposia*

### 2017-04-08 implementation.tex
.

We tabulate our preliminary evaluation in \tabref{res-rel}. We used
few of the benchmarks described in \cite{zutshi2014multiple},
including the Van der Pol oscillator, Brusselator, Lorenz attractor
and the Navigation benchmark. As before, we ran PWA-Rel $10$ times
with different seeds and averaged the results. We tabulate both the
total time taken and the time taken by SAL to compute the
counter-example and compare against an implementation of S3CAM. Note
that different abstraction parameters are used for S3CAM and
PWA-Rel, due to the differences in which they operate.

\begin{table}[!htbp]
\centering
\caption{Avg. timings for benchmarks. The \textbf{BMC} column lists
time taken by the BMC engine. The total time in seconds (rounded off
to an integer) is noted under \textbf{PWA-Rel} and \textbf{S3CAM}.
$TO$ signifies time $>5hr$, after which the search was killed.}
\label{tab:res-rel}
\begin{tabular}{@{}llll@{}}
\toprule
    Benchmark & PWA Rel + BMC & PWA Rel + LP & S3CAM\\
\midrule
    Van der Pol ($\prop_3$)   &$14$ & $20$ & $24$\\
    Brusselator               &$4$ & $4$ & $2$\\
    Lorenz                    &$122$ & $120$ & $35$\\
%B.Ball                    &  &   & \\
    Nav ($\prop_P$)           &$TO$ & $1710$  & $603$ \\%9423 + 4480
    Nav ($\prop_Q$)           &$TO$ & $1560$   & $546$ \\%8105 + 970
    Nav ($\prop_R$)           &$TO$ & $2352$  & $2003$\\
    Nav ($\prop_S$)           &$TO$ & $0$  & $2100$\\
    Bouncing Ball             &$Safe$ & $Safe$  & $450$\\

@@

The results show promise, but the performance is comparable. Also,
PWA-Rel timed out on some benchmarks like Nav $\prop_R$, Nav $\prop_S$
and the bouncing ball. However, we need to explore more benchmarks to
be conclusive. PWA-Rel's performance can be explained by the
difficulty in finding a good abstraction ($\quant_\epsilon$), which
needs to be fine enough, to obtain good prediction models but coarse
enough, to be manageable by the current SMT solvers. Specifically, to
obtain a good quality counter-example from the model checker (and
avoid false positives), the transition system should be created from
models with high accuracy, for which a finer abstraction is required.
However, the exploration of a finer abstraction is exponentially more
complex and results in a much bigger transition system, which the
current state of the art bounded model checkers (which use SMT
solvers) can not handle under reasonable resources.

>>>>

We tabulate our preliminary evaluation in \tabref{res-rel}. We used
the more difficult benchmarks described in \cite{zutshi2014multiple},
including the Van der Pol oscillator, Brusselator, Lorenz attractor
and the Navigation benchmark. PWA-Rel and S3CAM were ran $10$ times
with different seeds and the running times were averaged. We tabulate
both the total time taken by PWA-Rel+SAL and PWA-Rel+LP to compute the
counter-example and compare against an implementation of S3CAM.
Different abstraction parameters are used for S3CAM and PWA-Rel, due
to the differences in which they operate. PWA-Rel requires a finer
abstraction to begni with in order to minimize the modeling errors.
On the other hand, a coarser abstraction as the intital abstraction is
works better for S3CAM due to the expensive refinement procedure
involved.

\begin{table}[!htbp]
\centering
\caption{Avg. timings for benchmarks. The \textbf{BMC} column lists
time taken by the BMC engine. The total time in seconds (rounded off
to an integer) is noted under \textbf{PWA-Rel} and \textbf{S3CAM}.
$TO$ signifies time $>5hr$, after which the search was killed.}
\label{tab:res-rel}
\begin{tabular}{@{}llll@{}}
\toprule
    Benchmark & PWA Rel + SAL & PWA Rel + LP & S3CAM\\
\midrule
    Van der Pol ($\prop_3$)   &$0.2$ & $0.34$ & $0.4$\\
    Brusselator               &$0.06$ & $0.06$ & $0.03$\\
    Lorenz                    &$0.4$ & $0.33$ & $0.58$\\
%B.Ball                    &  &   & \\
    Nav ($\prop_P$)           &$TO$ & $28.5$  & $10$ \\%9423 + 4480
    Nav ($\prop_Q$)           &$TO$ & $26$   & $9.1$ \\%8105 + 970
    Nav ($\prop_R$)           &$TO$ & $39.2$  & $33.3$\\
    Nav ($\prop_S$)           &$TO$ & $71$  & $35$\\
    Bouncing Ball             &$Safe$ & $Safe$  & $7.5$\\

@@

As apparent form the results, the performance is comparable in all
benchmarks, but the last one: bouncing ball. PWA-Rel determines it to
be `safe' as it can not find a counter-example. Also, PWA-Rel performs
better with the LP solver as PWA-Rel+SAL times out on most of the
benchmarks. However, we need to explore more benchmarks to
be conclusive. PWA-Rel's performance can be explained by the
difficulty in finding a good abstraction ($\quant_\epsilon$), which
needs to be fine enough, to obtain good prediction models but coarse
enough, to be manageable by the current SMT solvers. Specifically, to
obtain a good quality counter-example from the model checker (and
avoid false positives), the transition system should be created from
models with high accuracy, for which a finer abstraction is required.
However, the exploration of a finer abstraction is exponentially more
complex and results in a much bigger transition system, which the
current state of the art bounded model checkers (which use SMT
solvers) can not handle under reasonable resources.
